Open archaeology, open source?

### 2024-01-31 analysis/_06-network.qmd
Export graphs as gexf

# Network stats (ignoring isolates)
graph_n_repos <- length(oarch_graph_repo_repo)
graph_n_users <- length(oarch_graph_user_user)
```

>>>>

# Network stats (ignoring isolates)
graph_n_repos <- length(oarch_graph_repo_repo)
graph_n_users <- length(oarch_graph_user_user)

# Export as gexf
write.gexf(igraph.to.gexf(oarch_graph_repo_user), 
           output = here("analysis/data/derived_data/oarch_repo_user.gexf"))
write.gexf(igraph.to.gexf(oarch_graph_repo_repo), 
           output = here("analysis/data/derived_data/oarch_repo_repo.gexf"))
write.gexf(igraph.to.gexf(oarch_graph_user_user), 
           output = here("analysis/data/derived_data/oarch_user_user.gexf"))
```

### 2024-01-31 analysis/openarchaeo_collaboration.qmd
Export graphs as gexf

library("english")
library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("gt")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("scales")
library("tidygraph")
library("tidyverse")
```

>>>>

library("english")
library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```
